### 2018-09-08 Sections/errors_in_quantum_networks.tex
Tidy up, corrected some errors
Added T2 time

Consecutive dephasing channels act multiplicatively as,
\begin{align} \label{eq:multi_deph}
\mathcal{E}_{p_1}^\mathrm{dephasing} \circ \mathcal{E}_{p_2}^\mathrm{dephasing} = \mathcal{E}_{p_1 p_2}^\mathrm{dephasing}.
\end{align}

@@

A qubit dephasing channel is often quoted in terms of its $T_2$-time\index{T$_2$-time}, a characteristic time for dephasing to occur under continuous time-evolution.

@@

>>>>

Consecutive dephasing channels accumulate into another dephasing channel,
\begin{align} \label{eq:multi_deph}
\mathcal{E}_{p_1}^\mathrm{dephasing} \circ \mathcal{E}_{p_2}^\mathrm{dephasing} = \mathcal{E}_{p'}^\mathrm{dephasing},
\end{align}
where,
\begin{align}
	p' = p_1 p_2 + (1-p_1)(1-p_2).
\end{align}

@@

A qubit dephasing channel is often quoted in terms of its $T_2$-time\index{T$_2$-time}, a characteristic time for dephasing to occur under continuous time-evolution. Specifically, the probability of no dephasing occuring scales as,
\begin{align}
p_\mathrm{no\,error} = e^{-\frac{t}{T_2}},	
\end{align}
as shown in Fig.~\ref{fig:T2_time}.

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{T2_time}
	\caption{Dephasing under continuous-time evolution, with characteristic decay rate given by the $T_2$-time. $p_\mathrm{no\,error}$ is the probability that the state is left unchanged, whereas \mbox{$1-p_\mathrm{no\,error}$} is the probability that it is replaced with the completely dephased state.}\label{fig:T2_time}
\end{figure}

@@

In the specific context of optics, the loss channel (Sec.~\ref{sec:eff_err})\index{Loss channel} is the equivalent of amplitude damping.
